A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-08-11 response_letter.tex

\textcolor{blue}{We feel we have now more clearly outlined the structure of the paper by including an updated figure one explicitly showing the breakdown of the chapters and their link to foraging ecology. This also more clearly highlights the novel aspect of our review, of building a qualitative framework base on foraging ecology to identify the potential levels of scavenging in extinct species and systems and pointing towards possible methods to better focus on certain systems, such as energetic models.}

Here are some specific issues that should be addressed in my opinion:

\begin{enumerate}
\item{Abstract: Scavenging can be difficult to observe, but probably no more so than predation.
Also, using experimental carcasses, scavenging is actually quite easy to observe.}

\textcolor{blue}{We emphasise that food webs have tended to lump all carnivory into predation and it is with extinct species that we have no observational evidence.
We now note measures often used in dietary analysis, such as stomach contents and stable isotope analysis, are unable to distinguish between scavenging and predation. We emphasis that the subsequent need for extensive behavioral data has led to food webs tending to lump all carnivory into predation and this is particularly likely with extinct species. (page 1, lines 11-16)}

@@

\item{Page 9: It is true that carrion can comprise a large percentage of a hyena's diet, but your text seems misleading. Most studies have shown that most of a hyena's diet is from predation. For example, see Cooper et al. (1999; Afr. J. Ecol. 37:149–160) and Gasaway et al. (1991; Afr. J. Ecol. 29: 64–75).}

\textcolor{blue}{We have clarified this point about hyenas to say it is their ability to take large proportions of carrion under certain circumstances that makes them a useful focal species: \textit{``The particular ability of hyenas to subsist on high proportions of carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms.''}}

\item{Your section on Handling Time is so short that I think it should be cut or combined with another section.}

\textcolor{blue}{The hierarchy of our paper wasn't clear as we intended in the first version but thanks to the review process we have now clarified that this is the opening paragraph to a larger section which has subsections e.g. food processing (see also updated figure 1).}

@@

\textcolor{blue}{It is undoubtedly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this capacity to scavenge  a high proportion of their diet possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version. 
As we note in the above comment, a combination of a species' traits, and the state of the ecosystem they find themselves in will determine their scale of scavenging. 
Search rates can be altered by environmmetal or ecological conditions as well as intrinsic traits of the forager. 
So, far from invalidating our idea, it reinforces it.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species, which themselves are likely to be extremely variable; we are following this approach when we make inferences about ancient systems.}
\bigskip

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.
\bigskip

\textcolor{blue}{We agree it is more difficult to infer behavior with lower quality data. However by mapping out the variables that are likely to driver high levels of scavenging, such as in Figure 1, the absence of data for particular variblese, sfor example, will highlight the extra caution needed when inferring the existence of scavenging in such a particular circumstance.}
\textcolor{blue}{Figure 2 has been removed and figure 1 has been expanded.}
